---
title: "IV Valid Test"
author: Kanta Ogawa
date: "2022 / 03 / 14"
output: html_document
---

```{r read data, echo=FALSE, include=FALSE }

library(dplyr)
library(tidyr)
library(ggmap)
library(lmtest)
library(stargazer)
library(readr)
library(xtable)
library(ggplot2)

library(AER)
# library(sandwitch)


df <- read.csv("../Data/panel_data.csv")


```

```{r preprocess, echo=FALSE, include=FALSE }

## 1.Explanatory variable: Relative_redistributive_effects

df_unbalance_GINI <- df[!is.na(df$Relative_redistributive_effects) &
  !is.na(df$Elderly_pct) &
  !is.na(df$Right_left) & # Include the political data
  !is.na(df$Chrstprotpct) &
  !is.na(df$Unemployment_rate_pct) & # contorol var
  !is.na(df$Poverty_rate), ] # control var

df_unbalance_GINI_count <- df_unbalance_GINI %>%
  group_by(LOCATION) %>%
  summarise(count = n())

df_unbalance_GINI_one <- df_unbalance_GINI_count[df_unbalance_GINI_count$count == 1, ]

for (i in df_unbalance_GINI_one$LOCATION) {
  df_unbalance_GINI <- df_unbalance_GINI[df_unbalance_GINI$LOCATION != i, ]
}

df_unbalance_GINI_timecount <- df_unbalance_GINI %>%
  group_by(TIME) %>%
  summarise(timecount = n()) # each period is higher than 3 - OK

df_unbalance_GINI_timeone <- df_unbalance_GINI_timecount[df_unbalance_GINI_timecount$timecount == 1, ]


for (t in df_unbalance_GINI_timeone$TIME) {
  df_unbalance_GINI <- df_unbalance_GINI[df_unbalance_GINI$TIME != t, ]
}


## 2.Explanatory variable: Public Transfer

df_unbalance_pub <- df[!is.na(df$Public_transfer) &
  !is.na(df$Elderly_pct) &
  !is.na(df$Right_left) & # Include the political data
  !is.na(df$Chrstprotpct) &
  !is.na(df$Unemployment_rate_pct) & # contorol var
  !is.na(df$Poverty_rate), ] # control var

df_unbalance_pub_count <- df_unbalance_pub %>%
  group_by(LOCATION) %>%
  summarise(count = n())

df_unbalance_pub_one <- df_unbalance_pub_count[df_unbalance_pub_count$count == 1, ]

for (i in df_unbalance_pub_one$LOCATION) {
  df_unbalance_pub <- df_unbalance_pub[df_unbalance_pub$LOCATION != i, ]
}

df_unbalance_pub_timecount <- df_unbalance_pub %>%
  group_by(TIME) %>%
  summarise(timecount = n())

df_unbalance_pub_timeone <- df_unbalance_pub_timecount[df_unbalance_pub_timecount$timecount == 1, ]


for (t in df_unbalance_pub_timeone$TIME) {
  df_unbalance_pub <- df_unbalance_pub[df_unbalance_pub$TIME != t, ]
}


## 3. Net Public Transfer?

df_unbalance_netpub <- df[!is.na(df$Net_public_transfer) &
  !is.na(df$Elderly_pct) &
  !is.na(df$Right_left) & # Include the political data
  !is.na(df$Chrstprotpct) &
  !is.na(df$Unemployment_rate_pct) & # contorol var
  !is.na(df$Poverty_rate), ] # control var

df_unbalance_netpub_count <- df_unbalance_netpub %>%
  group_by(LOCATION) %>%
  summarise(count = n())

df_unbalance_netpub_one <- df_unbalance_netpub_count[df_unbalance_netpub_count$count == 1, ]

for (i in df_unbalance_netpub_one$LOCATION) {
  df_unbalance_netpub <- df_unbalance_netpub[df_unbalance_netpub$LOCATION != i, ]
}

df_unbalance_netpub_timecount <- df_unbalance_netpub %>%
  group_by(TIME) %>%
  summarise(timecount = n()) # each period is higher than 3 - OK

df_unbalance_netpub_timeone <- df_unbalance_netpub_timecount[df_unbalance_netpub_timecount$timecount == 1, ]


for (t in df_unbalance_netpub_timeone$TIME) {
  df_unbalance_netpub <- df_unbalance_netpub[df_unbalance_netpub$TIME != t, ]
}

```




```{r, echo=FALSE}

# A. IV: Elderly_pct

## i.  Ex var:  Relative_redistributive_effects

mod_Eld_GINI <- lm(Relative_redistributive_effects ~ 1
  + Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia omit
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Elderly_pct,
data = df_unbalance_GINI
)



Eld_GINI <- linearHypothesis(mod_Eld_GINI,
  "Elderly_pct = 0",
  vcov = vcovHC, type = "HC3"
)




## ii.  Ex var:  Public transfer

mod_Eld_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Elderly_pct,
data = df_unbalance_pub
)


Eld_pub <- linearHypothesis(mod_Eld_pub,
  "Elderly_pct = 0",
  vcov = vcovHC, type = "HC3"
)

## iii.  Ex var: Net Public transfer

mod_Eld_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  + Elderly_pct,
data = df_unbalance_netpub
)


Eld_netpub <- linearHypothesis(mod_Eld_netpub,
  "Elderly_pct = 0",
  vcov = vcovHC, type = "HC3"
)

```





```{r, echo=FALSE}

# B. IV: Right_left

## i.  Ex var:  Relative_redistributive_effects


mod_Rile_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Right_left,
data = df_unbalance_GINI
)



Rile_GINI <- linearHypothesis(mod_Rile_GINI,
  "Right_left = 0",
  vcov = vcovHC, type = "HC3"
)


## ii.  Ex var:  Public transfer

mod_Rile_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Right_left,
data = df_unbalance_pub
)



Rile_pub <- linearHypothesis(mod_Rile_pub,
  "Right_left = 0",
  vcov = vcovHC, type = "HC3"
)



## iii.  Ex var: Net Public transfer

mod_Rile_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  + Right_left,
data = df_unbalance_netpub
)



Rile_netpub <- linearHypothesis(mod_Rile_netpub,
  "Right_left = 0",
  vcov = vcovHC, type = "HC3"
)

```



```{r, echo=FALSE}

# C. IV: Welfare

## i.  Ex var:  Relative_redistributive_effects


mod_Wel_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Welfare,
data = df_unbalance_GINI
)


Wel_GINI <- linearHypothesis(mod_Wel_GINI,
  "Welfare = 0",
  vcov = vcovHC, type = "HC3"
)


## ii.  Ex var:  Public transfer

mod_Wel_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Welfare,
data = df_unbalance_pub
)



Wel_pub <- linearHypothesis(mod_Wel_pub,
  "Welfare = 0",
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Wel_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
 +Chrstprotpct
 +Chrstcatpct
 +Chrstorthpct
 +Islam_general_pct
 +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  + Welfare,
data = df_unbalance_netpub
)



Wel_netpub <- linearHypothesis(mod_Wel_netpub,
  "Welfare = 0",
  vcov = vcovHC, type = "HC3"
)

```



```{r, echo=FALSE}


# D. IV: Equality_positive

## i.  Ex var:  Relative_redistributive_effects

mod_Equal_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Equality_pos,
data = df_unbalance_GINI
)



Equal_GINI <- linearHypothesis(mod_Equal_GINI,
  "Equality_pos = 0",
  vcov = vcovHC, type = "HC3"
)



## ii.  Ex var:  Public transfer

mod_Equal_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Equality_pos,
data = df_unbalance_pub
)



Equal_pub <- linearHypothesis(mod_Equal_pub,
  "Equality_pos = 0",
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Equal_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  + Equality_pos,
data = df_unbalance_netpub
)

Equal_netpub <- linearHypothesis(mod_Equal_netpub,
  "Equality_pos = 0",
  vcov = vcovHC, type = "HC3"
)


```




```{r, echo=FALSE}

# E. IV: Elderly_pct & Right_left

## i.  Ex var:  Relative_redistributive_effects

mod_Eld_Rile_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  +  Right_left
  + Elderly_pct,
data = df_unbalance_GINI
)



Eld_Rile_GINI <- linearHypothesis(mod_Eld_Rile_GINI,
 c("Right_left = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)





## ii.  Ex var:  Public transfer

mod_Eld_Rile_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  +  Right_left
  + Elderly_pct,
data = df_unbalance_pub
)



Eld_Rile_pub <- linearHypothesis(mod_Eld_Rile_pub,
  c("Right_left = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Eld_Rile_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  +  Right_left
  + Elderly_pct,
data = df_unbalance_netpub
)

Eld_Rile_netpub <- linearHypothesis(mod_Eld_Rile_netpub,
  c("Right_left = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


```

```{r, echo=FALSE}

#  F. IV: Elderly_pct & Welfare

## i.  Ex var:  Relative_redistributive_effects

mod_Eld_Wel_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Elderly_pct
  + Welfare,
data = df_unbalance_GINI
)



Eld_Wel_GINI <- linearHypothesis(mod_Eld_Wel_GINI,
 c("Welfare = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)





## ii.  Ex var:  Public transfer

mod_Eld_Wel_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Elderly_pct
  + Welfare,
data = df_unbalance_pub
)



 Eld_Wel_pub <- linearHypothesis(mod_Eld_Wel_pub,
  c("Welfare = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Eld_Wel_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  + Elderly_pct
  + Welfare,
data = df_unbalance_netpub
)

Eld_Wel_netpub <- linearHypothesis(mod_Eld_Wel_netpub,
  c("Welfare = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


```



```{r, echo=FALSE}

#  G. IV: Elderly_pct & Equality_pos

## i.  Ex var:  Relative_redistributive_effects

mod_Eld_Equ_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Elderly_pct
  + Equality_pos,
data = df_unbalance_GINI
)



Eld_Equ_GINI <- linearHypothesis(mod_Eld_Equ_GINI,
 c("Equality_pos = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)





## ii.  Ex var:  Public transfer

mod_Eld_Equ_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  + Elderly_pct
  + Equality_pos,
data = df_unbalance_pub
)



 Eld_Equ_pub <- linearHypothesis(mod_Eld_Equ_pub,
  c("Equality_pos = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Eld_Equ_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  + Elderly_pct
  + Equality_pos,
data = df_unbalance_netpub
)

Eld_Equ_netpub <- linearHypothesis(mod_Eld_Equ_netpub,
  c("Equality_pos = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


```



```{r, echo=FALSE}

#  H. IV: Elderly_pct & Welfare & Equality_pos

## i.  Ex var:  Relative_redistributive_effects

mod_Eld_Wel_Equ_GINI <- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  +Elderly_pct
  + Welfare
  + Equality_pos,
data = df_unbalance_GINI
)



Eld_Wel_Equ_GINI <- linearHypothesis(mod_Eld_Wel_Equ_GINI,
 c("Equality_pos = 0","Welfare = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)





## ii.  Ex var:  Public transfer

mod_Eld_Wel_Equ_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  +Elderly_pct
  + Welfare
  + Equality_pos,
data = df_unbalance_pub
)



 Eld_Wel_Equ_pub <- linearHypothesis(mod_Eld_Wel_Equ_pub,
  c("Equality_pos = 0","Welfare = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Eld_Wel_Equ_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  +Elderly_pct
  + Welfare
  + Equality_pos,
data = df_unbalance_netpub
)

Eld_Wel_Equ_netpub <- linearHypothesis(mod_Eld_Wel_Equ_netpub,
  c("Equality_pos = 0","Welfare = 0","Elderly_pct= 0"),
  vcov = vcovHC, type = "HC3"
)


```


```{r, echo=FALSE}

#  J. IV: Election year

## i.  Ex var:  Relative_redistributive_effects

mod_Ele_year_GINI<- lm(Relative_redistributive_effects ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Bulgaria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Romania
  + Russia
  + Slovakia
  + Slovenia
  + South_Africa
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 30 countries
  + y2005 # omit y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011 # omit 2010
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  +Election_year,
data = df_unbalance_GINI
)



Ele_year_GINI <- linearHypothesis(mod_Ele_year_GINI,
 "Election_year = 0",
  vcov = vcovHC, type = "HC3"
)





## ii.  Ex var:  Public transfer

mod_Ele_year_pub <- lm(Public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Australia
  + Austria
  + Belgium
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Lithuania
  + Luxembourg
  + Mexico
  + New_Zealand
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 26 countries
  + y1992 # y1991
  + y1993
  + y1994
  + y1995
  + y1996
  + y1997
  + y1998
  + y1999
  + y2000
  + y2001
  + y2002
  + y2003
  + y2004
  + y2005
  + y2006
  + y2007
  + y2008
  + y2009
  + y2010
  + y2011
  + y2012
  + y2013
  + y2014
  + y2015
  + y2016
  + y2017
  + y2018
  + y2019
  +Election_year,
data = df_unbalance_pub
)



 Ele_year_pub <- linearHypothesis(mod_Ele_year_pub,
  "Election_year = 0",
  vcov = vcovHC, type = "HC3"
)


## iii.  Ex var: Net Public transfer

mod_Ele_year_netpub <- lm(Net_public_transfer ~ 1
+ Poverty_rate
  + Unemployment_rate_pct
  + Poverty_rate
  +Chrstprotpct
  +Chrstcatpct
  +Chrstorthpct
  +Islam_general_pct
  +Buddism_general
  #+ Austria
  + Canada
  + Czech_Republic
  + Estonia
  + Finland
  + Germany
  + Hungary
  + Ireland
  + Israel
  + Italy
  + Luxembourg
  + Norway
  + Poland
  + Portugal
  + Republic_of_Korea
  + Slovakia
  + Slovenia
  + Switzerland
  + Turkey
  + United_Kingdom
  + United_States_of_America # 21 countries
  + y1997 # omit y1995
  + y1999
  + y2001
  + y2003
  + y2005
  + y2007
  + y2009
  + y2011
  + y2013
  + y2015
  + y2017
  +Election_year,
data = df_unbalance_netpub
)

Ele_year_netpub <- linearHypothesis(mod_Ele_year_netpub,
  "Election_year = 0",
  vcov = vcovHC, type = "HC3"
)


```




```{r, echo=FALSE,results='asis'}
#縦に並ぶ



data <- matrix(c(
  Eld_GINI[2, 3],
  Rile_GINI[2, 3],
  Wel_GINI[2, 3],
  Equal_GINI[2, 3],
  Eld_Rile_GINI[2, 3],
  #Eld_Wel_GINI[2, 3],
  #Eld_Equ_GINI[2, 3],
  Eld_Wel_Equ_GINI[2, 3],
  #Ele_year_GINI[2,3],
  Eld_pub[2, 3],
  Rile_pub[2, 3],
  Wel_pub[2, 3],
  Equal_pub[2, 3],
  Eld_Rile_pub[2, 3],
  #Eld_Wel_pub[2, 3],
  #Eld_Equ_pub[2, 3],
  Eld_Wel_Equ_pub[2, 3],
  #Ele_year_pub[2,3],
  Eld_netpub[2, 3],
  Rile_netpub[2, 3],
  Wel_netpub[2, 3],
  Equal_netpub[2, 3],
  Eld_Rile_netpub[2, 3],
  #Eld_Wel_netpub[2, 3],
  #Eld_Equ_netpub[2, 3],
  Eld_Wel_Equ_netpub[2, 3]
  #Ele_year_netpub[2,3]
), 6, 3)


colnames(data) <- c("----Relative redistributive effects---- ", "----Public transfer----", "----Net public transfer----")

rownames(data) <- c(
  "IV1:Elderly rate %",
  "IV2:Right left of politics",
  "IV3:Welfare of politics",
  "IV4:Equality positiveness",
  "IV5:Elderly rate (%) and Right left of politics", #"Elderly rate (%) and Welfare of politics",
   #"Elderly rate (%) and Equality positiveness of politics",
   "IV6:Elderly rate (%), Welfare and Equality positiveness"
   #"Election yeat"
)


stargazer(data,
  type = "html",
  title = "IV valid test",
  notes = "columns: Instrumental variables, rows: Explanatory variables"

)

stargazer(data,
  type = "latex",
  out = "../Code/a.IV_new.tex",
  title = "IV valid test",
  notes = "columns: Instrumental variables, rows: Explanatory variables"
)
```





```{r, echo=FALSE,results='asis'}


#縦に並べる

data_new <- matrix(c(
  cor(df_unbalance_GINI$Relative_redistributive_effects, df_unbalance_GINI$Elderly_pct),
  cor(df_unbalance_GINI$Relative_redistributive_effects, df_unbalance_GINI$Right_left),
  cor(df_unbalance_GINI$Relative_redistributive_effects, df_unbalance_GINI$Welfare),
  cor(df_unbalance_GINI$Relative_redistributive_effects, df_unbalance_GINI$Equality_pos),
  cor(df_unbalance_pub$Public_transfer, df_unbalance_pub$Elderly_pct),
  cor(df_unbalance_pub$Public_transfer, df_unbalance_pub$Right_left),
  cor(df_unbalance_pub$Public_transfer, df_unbalance_pub$Welfare),
  cor(df_unbalance_pub$Public_transfer, df_unbalance_pub$Equality_pos),
  cor(df_unbalance_netpub$Net_public_transfer, df_unbalance_netpub$Elderly_pct),
  cor(df_unbalance_netpub$Net_public_transfer, df_unbalance_netpub$Right_left),
   cor(df_unbalance_netpub$Net_public_transfer, df_unbalance_netpub$Welfare),
   cor(df_unbalance_netpub$Net_public_transfer, df_unbalance_netpub$Equality_pos)
), 4, 3)


colnames(data_new) <- c("----Relative redistributive effects---- ", "----Public transfer----", "----Net public transfer----")

rownames(data_new) <- c("Elderly rate %", "Right left of politics", "Welfare of politics", "Equality positiveness")


stargazer(data_new,
  type = "html",
  title = "IV correlation check",
  notes = "columns: Instrumental variables, rows: Explanatory variables"
)

stargazer(data_new,
  type = "latex",
  title = "IV correlation check",
  notes = "columns: Instrumental variables, rows: Explanatory variables"
)
```








```{r, echo=FALSE,results='asis'}
#縦に並ぶ



data <- matrix(c(
  Eld_GINI[2, 3],
  Rile_GINI[2, 3],
  Wel_GINI[2, 3],
  Equal_GINI[2, 3],
  Eld_Rile_GINI[2, 3],
  #Eld_Wel_GINI[2, 3],
  #Eld_Equ_GINI[2, 3],
  Eld_Wel_Equ_GINI[2, 3],
  #Ele_year_GINI[2,3],
  Eld_pub[2, 3],
  Rile_pub[2, 3],
  Wel_pub[2, 3],
  Equal_pub[2, 3],
  Eld_Rile_pub[2, 3],
  #Eld_Wel_pub[2, 3],
  #Eld_Equ_pub[2, 3],
  Eld_Wel_Equ_pub[2, 3],
  #Ele_year_pub[2,3],
  Eld_netpub[2, 3],
  Rile_netpub[2, 3],
  Wel_netpub[2, 3],
  Equal_netpub[2, 3],
  Eld_Rile_netpub[2, 3],
  #Eld_Wel_netpub[2, 3],
  #Eld_Equ_netpub[2, 3],
  Eld_Wel_Equ_netpub[2, 3]
  #Ele_year_netpub[2,3]
), 6, 3)


colnames(data) <- c("----Relative redistributive effects---- ", "----Public transfer----","k")

rownames(data) <- c(
  "IV1:Elderly rate %",
  "IV2:Right left of politics",
  "IV3:Welfare of politics",
  "IV4:Equality positiveness",
  "IV5:Elderly rate (%) and Right left of politics",
   "IV6:Elderly rate (%), Welfare and Equality positiveness"

)


stargazer(data,
  type = "html",
  title = "IV valid test",
  notes = "rows: Instrumental variables, columns: Explanatory variables",
  dep.var.caption = "Target variables"


)
